---
title: "Relationship between Life Expectancy, GDP per Capita, and Population for Canada"
---

I decided to focus the next analysis on Canada. I will be visualizing `life_expectancy`, `gpp_per_capita`, and `population_millions` over time in Canada.

```{r}
#| label: setup
#| include: false

pacman::p_load(tidyverse, readr, ggplot2)
gapminder <- read_csv("./gapminder.csv")

```

```{r}
#| label: fig-canadalife
#| echo: false
#| message: false
#| warning: false
#| fig.cap: "This is a scatter plot showing the life expectancy over time in Canada"

ggplot(data=filter(gapminder, country == "Canada"), aes(x=year, y=life_expectancy)) +
  geom_line() +
  labs(title="Life Expectancy over Time in Canada",
       x="Years",
       y="Life Expectancy (years)")

```

In @fig-canadalife you can see life expectancy has increased over time in Canada.

```{r}
#| label: fig-canadagdp
#| echo: false
#| message: false
#| warning: false
#| fig.cap: "This is a scatter plot showing the GDP per Capita over time in Canada"

ggplot(data=filter(gapminder, country == "Canada"), aes(x=year, y=gdp_per_capita)) +
  geom_line() +
  labs(title="GDP per Capita over Time in Canada",
       x="Years",
       y="GDP per Capita (dollars)")

```

In @fig-canadagdp you can see GDP per capita has increased over time in Canada.

```{r}
#| label: fig-canadapop
#| echo: false
#| message: false
#| warning: false
#| fig.cap: "This is a scatter plot showing the population over time in Canada"

ggplot(data=filter(gapminder, country == "Canada"), aes(x=year, y=population_millions)) +
  geom_line() +
  labs(title="Population over Time in Canada",
       x="Years",
       y="Population (Millions)")

```

In @fig-canadapop you can see life expectancy has increased over time in Canada.