---
title: "Gapminder Analysis"
---

This website will contain preliminary analysis of the `Gapminder` dataset. The `Gapminder` dataset contains information on 142 countries from 1952 to 2007 in 5-year intervals. The variables available to analyze are: `country`, `continent`, `year`, `life_expectancy`, `population_millions`, and `gpd_per_capita`. Below, you can see the first six lines of the dataset.

```{r}
#| label: setup
#| include: false

pacman::p_load(tidyverse, readr, ggplot2)

```


```{r}
#| label: dataset
#| message: false
#| warning: false
gapminder <- read_csv("./gapminder.csv")
head(gapminder)
```

Below you will find links to the other pages:

  - [About](https://ejinright.github.io/qtm350-quiz02/about.html)
  
  - [Life Expectancy and GDP per Capita](https://ejinright.github.io/qtm350-quiz02/life-gdp.html)

  - [Life Expectancy and Population](https://ejinright.github.io/qtm350-quiz02/life-population.html)

  - [Country Analysis](https://ejinright.github.io/qtm350-quiz02/country.html)
